Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-14 Ben_Manuscripts/structure_paper/supporting_information.tex
Draft updates + PMF stuff
edits

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}

@@

  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

@@

@@

@@

@@

  Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
  radical polymerization (Figure~\ref{fig:xlink_mech}).  Head-to-tail addition
  takes place between terminal vinyl groups on each of the monomer tails.  We
  only considered head-to-tail addition since it is the dominant propagation mode
  in the real system.

@@

@@

>>>>

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
%\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}

@@

%  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

@@

  \section{Number of monomers per column}\label{section:monomers_per_column}

  We chose to build all systems using 20 monomers per column. We made this choice
  by considering a number of factors that directly affect the quality of our results. 
  Clearly, choosing a small number of layers will cause the system to suffer from 
  finite size effects. Even in our 20 monomer-per-column system, axial correlations
  between stacked monomers persist throughout the entire correlation function (See
  Figure ~\ref{M-fig:correlation}). The correlation function of the system which we
  built with 40 monomers per column continues to oscillate for its full length
  (Figure~\ref{fig:tall_correlation_full}). If we continue adding monomers, the 
  correlation function will eventually fully decay but it is not worth the 
  computational expense. Regardless, the correlation lengths calculated from 20
  monomer per column simulations are in sufficient agreement with experiment.

  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{tall_correlation_full.png}
  \caption{Oscillations persist throughout the length of the correlation 
  function for the sandwiched system in the ordered basin built with 40 monomers
  per column. The full system is ca. 17 nm tall so the full correlation function
  covers half this length since periodicity forces the remaining length to be its
  mirror image.}\label{fig:tall_correlation_full}
  \end{figure}

  We may be able to simulate systems using less than 20 monomers per column, but chose
  to use 20 since it gives fairly good resolution when simulating X-ray diffraction 
  patterns. The size of the fourier space bin in each dimension is determined by 
  $dfrac{2\pi}{L}$ where L is the length of a given box vector. The z-box vector 
  for 20 monomer-per-column systems is $\approx$ 85 \AA which means we will see 
  a reciprocal space resolution of 0.074 \AA$^{-1}$ in the z direction. Further decreasing
  the resolution would increase the noise in the simulated patterns and make it more
  difficult to measure the intensity of reflections of interest.

@@

  \section{Equilibration Details}\label{section:equilibration}

  We developed equilibration schemes to create dry and wet configurations. Both
  schemes start with an initial configuration generated according to the previous
  guidelines. To create a dry configuration, we fix monomer head groups in the
  sandwiched or parallel-displaced configuration using position restraints with a
  force constant of 10$^6$ kJ mol$^{-1}$ nm$^{-2}$. We run a 50 ps simulation in
  the NVT ensemble which allows the monomer tails to settle without disrupting
  the ordering of the head groups. Doing so also mitigates system dependence on
  initial monomer configuration. Every 50 ps, we reduce the force constants by
  the square root of its previous value. Once the force constant is below 10 KJ
  mol$^{-1}$ nm$^{-2}$, we reduce the restraints in a sequence with values of
  8, 3, 2, 1, and 0 KJ mol$^{-1}$ nm$^{-2}$ respectively. We allow the resulting
  unrestrained structure to equilibrate for 5 ns in the NPT ensemble
  with pressure controlled by the berendsen barostat. Next, we run long NPT
  equilibration simulations for at least 400 ns using the Parrinello-Rahman
  barostat with a time constant of 10 ps.

  % MRS6: some parameters missing here (time run between insertions, etc). 
  % I assume they are in supporting information?
  % BJC5: all water is present in initial configuration. This did not follow the more
  % complex procedures that I've come up with since then. 
  In order to create a ``wet'' system, we solvated an initial configuration with
  water using \texttt{gmx solvate}. We remove all water molecules placed outside
  the pore region. Then we randomly remove water molecules inside the pore region
  until the pores reach the desired concentration of water. The remainder of the
  equilibration follows the same procedure as the dry system.

@@

  \section{Solvation}\label{section:solvation}

  % formatting taken from : https://tex.stackexchange.com/questions/239715/add-titles-for-rows-and-columns-in-a-subfloat
  \newlength{\tempdima}
  \newcommand{\rowname}[1]% #1 = text
  {\rotatebox{90}{\makebox[\tempdima][c]{\textbf{#1}}}}

  \renewcommand{\thesubfigure}{\alph{subfigure}}
  \newcommand{\mycaption}[1]% #1 = caption
  {\refstepcounter{subfigure}\textbf{(\thesubfigure) }{\ignorespaces #1}}

  \begin{figure}[!htb]
  \begin{subfigure}{0.915\textwidth}
  	\settoheight{\tempdima}{\includegraphics[width=.32\linewidth]{solvated_offset_rzplot_1.png}}%
  	\centering\begin{tabular}{@{}c@{ }c@{ }c@{ }c@{}}
  	&\textbf{1 wt\%} & \textbf{\hspace{2em}2.5 wt\%} & \textbf{5 wt\%} \\
  	\rowname{Parallel Displaced}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_25.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_offset_rzplot_5.png}\\[-1ex]
  	%&\mycaption{0.2} & \mycaption{0.2} & \mycaption{0.3}\\
  	\rowname{Sandwiched}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_1.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_25.png}&
  	\includegraphics[width=.28\linewidth,trim={1cm 0 1.3cm 0},clip]{solvated_layered_rzplot_5.png}\\[-1ex]
  	%\mycaption{0.5} & \mycaption{0.6} & \mycaption{0.7} \\
  	\end{tabular}
  \end{subfigure}
  \begin{subfigure}{0.075\textwidth}
  	\includegraphics[width=\textwidth]{colorbar_jet.png}
  \end{subfigure}
	\caption{Adding 1 wt \% water to the ordered basin dry systems causes an increase in the intensity
	R-spots. R-double becomes visible in the parallel displaced configuration. Additional amounts
	of water increase discrepancies with experiment} %MRS7:by increasing disorder?
  \label{fig:solvation}

  \end{figure}

@@

  Crosslinking of the the monomer Na-GA3C11 occurs by a UV initiated free
  radical polymerization (FRP) (Figure~\ref{fig:xlink_mech}). Head-to-tail addition
  takes place between terminal vinyl groups on each of the monomer tails. We
  only considered head-to-tail addition since it is the dominant propagation mode
  in the real system.

@@

  We based our cross-linking algorithm on the known reaction mechanism.
  FRPs require an initiator which bonds to the system, meaning new atoms are
  introduced into the system. For simplicity, we simulated the initiator as
  hydrogen and made it present in the simulation by including them as dummy atoms
  in all possible locations where an addition could occur. We carry out the
  cross-linking procedure iteratively. During each iteration, the algorithm
  selects eligible bonding carbon atoms based on a distance cut-off. The algorithm
  then updates the topology with new bonds and changes dummy hydrogen atoms to appropriate
  hydrogen atom types. We only considered head-to-tail addition
  due to its dominance in the real system \cite{young_introduction_2011}. We did
  not consider direction of attack because the resultant mixture is racemic.

  Our implementation requires long simulation times to achieve high cross-link 
  densities. A typical cross-linking procedure can take up to 24 hours. In
  order to collect equilibrated data, further NPT simulation is necessary. We
  typically run a cross-linked system for an additional 100 ns to allow the system
  to readjust. For those reasons we did not cross-link all systems tested.

  \section{Ionic Conductivity}\label{section:ionic_conductivity}

  In the main text, we calculated ionic conductivity using the Nernst Einstein 
  relationship. We also measured ionic conductivity using a second method, 
  termed the Collective Diffusion model, for robustness. The collective 
  diffusion model measures the movement of the collective variable, Q, which
  is defined as the amount of charge transfer through the system and can be 
  thought to represent the center of charge of the system. The conductance, 
  $\gamma$, of the system can be calculated as:
  \begin{equation}
	 \gamma = \dfrac{D_Q}{k_b T} 
	\label{eqn:collective_diffusion}
  \end{equation}
  $D_Q$ is the diffusion coefficient of the collective variable Q and is 
  calculated using the Einstein relation. We convert the resulting value
  to ionic conductivity by multiplying by channel length and dividing by
  the membrane cross sectional area. One can access a detailed derivation of 
  the model elsewhere\cite{liu_collective_2013}.

  \begin{figure}[!htb]
        \centering
        \includegraphics[width=0.5\linewidth]{Ionic_conductivity.png}
        \caption{The Collective Diffusion model and the nernst-einstein relation yield
        agreeing values of ionic conductivity for both types of ordered basin systems 
        simulated. Both methods estimate the value of the ionic conductivity to be an 
        order of magnitude higher than the experimental value. There is more noise in
        the collective diffusion model because there is inherently less data that 
        can be used for its calculation. For that reason, we use only the Nernst 
        Einstein relationship in the main text.}
        \label{fig:conductivity}
  \end{figure}

@@

%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{width=0.45\textwidth}
%  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
%  \caption{}\label{fig:rdouble_offset_solvated_rzplot}
%  \end{subfigure}
%  \begin{subfigure}{width=0.45\textwidth}
%  \includegraphics[width=\textwidth]{rzplot_pore1_removed.png}
%  \caption{}\label{fig:rzplot_pore1_removed}
%  \end{subfigure}
%  \caption{(a) The simulated diffraction pattern of a system simulated in an ordered basin 
%  parallel displaced configuration with 1 wt\% water shows R-double at $mathbf{q}=(0, 0.7) \AA^{-1}$.
%  (b) When we remove }\label{fig:pore1_removed}
%  \end{figure}
